Extending the WebID Protocol with Access Delegation

### 2012-08-03 paper.tex
Added example of different views on the same resource

\lstinputlisting[
    lastline=26,name=webid,style=turtle,float=htb,label=listing:webid1,
    basicstyle=\ttfamily\scriptsize,
    caption={Profile allowing three different agents to act as Romeo}
]{Listings/mutlipleKeys.ttl}

@@

But when the origin server (OS) is serving a number of different profiles and is acting on behalf of a number of different users, then we have two issues that need to be taken into account: an issue of data perspective and an efficiency issue.

First whenever $OS$ connects as $U_1$ to a service it has to place the data received in a seperate quad store from the one it 
stores data as when connecting to that resources as user $U_2$. This is because the resource may return different representations
depending on who is connecting to it - one representation for close friends perhaps, and one for more distant ones.

Secondly, Whenever the Origin Server needs to act on behalf of $U_1$ to a remote server $R$ it will need to open a new TLS connection to that server using the certificate $C_u1$ for that user.
For $N$ users this could require $N$ parallel connections to the same server $S$.
\todo{calculate how inefficient this is, and at what size of network this starts really become problematic}
\todo{ST: add disadvantages according to the requirements (identity)}

>>>>

\lstinputlisting[
    lastline=26,name=webid,style=turtle,float=htb,label=listing:multipleKeyProfile,
    basicstyle=\ttfamily\scriptsize,
    caption={Profile allowing three different agents to act as Romeo}
]{Listings/mutlipleKeys.ttl}

@@

But when the origin server $OS$ is serving a number of different profiles $P_1$, $P_2$, $P_3$, ... $P_n$ each identifying the N users $U_1$, $U_2$, $U_3$, ..., $U_n$ and is acting on behalf of a these users, as would be the case for a  company, government agency, school, educational instituion, charyity, football club, ... server, then we have two issues that need to be taken into account: first an issue of data perspective and an efficiency issue.

First whenever $OS$ connects as $U_1$ to a remote resource $R$ it has to place the data received in a seperate quad store from the one it stores data in as when connecting to  the same resurce $R$ as the different user $U_2$. 
This is because the resource may return different representations depending on who is connecting to it - one representation for close friends of the owner of $R$ perhaps, and one for more distant ones. 
This can be illustrated using N3 graphs, by specifying a relation between a yet to be invented vocabulary of views on a resource, and a graph (cf. Listing~\ref{listing:views})

\lstinputlisting[
    lastline=36,name=views,style=turtle,float=htb,label=listing:views,
    basicstyle=\ttfamily\scriptsize,
    caption={Views on Juliet's FOAF profile by Freedom Box Laurence, when acting as Romeo and when acting as Lord Montague }
]{Listings/views.n3}

Secondly, Whenever the Origin Server needs to act on behalf of $U_1$ to a remote server $R$ it will need to open a new TLS connection to that server using the certificate $C_{u1}$ for that user.
 this could require $N$ parallel connections to the same server $S$.
\todo{calculate how inefficient this is, and at what size of network this starts really become problematic}
\todo{ST: add disadvantages according to the requirements (identity)}
